### 2016-09-18 paper.tex
Use 'N' for number of blades in table for consistency
Fix table ref format; resolves #76

    \begin{tabular}{c|c|c|c|c|c}
        Name & Rotor type & $N_\mathrm{b}$ & $c/R$ & $Re_D$ & Used in \\
        \hline
        Sandia 2 m \cite{Blackwell1976} &  Darrieus  & 2--3 & 0.06--0.09 & $\sim 10^6$ & \cite{Roh2013,Bedon2014} \\
        Sandia 5 m \cite{Sheldahl1977} &  Darrieus  & 3 & 0.08 & $\sim 10^6$ & \cite{Antheaume2008,Bedon2014} \\
        Sandia 17 m \cite{Worstell1978} & Darrieus  & 2 & 0.06 & $\sim 10^7$ & \cite{Para1988,Orlandi2015,Bedon2014} \\
        Sandia 34 m \cite{Ashwill1992} & Darrieus  & 2 & 0.05 & $\sim 10^7$ & \cite{Liu1992,Murray2011,Bedon2014}  \\
        Strickland \emph{et al.} \cite{Strickland1981} & H & 1--3 & 0.15 & $\sim 10^5$ & \cite{Ponta2001,Scheurich2011b} \\
        Laneville and Vitecoq \cite{Laneville1986} & H & 2 & 0.13 & $\sim 10^6$ & \cite{Amet2009} \\
        Howell \emph{et al.} \cite{Howell2010} & H & 2--3 & 0.33 & $\sim 10^5$ & \cite{Joo2015} \\
        Mertens \cite{Mertens2003} & H & 2 & 0.21 & $\sim 10^5$ & \cite{Orlandi2015} \\
        VAWT 850 \cite{Mays1990} & Tapered H & 2 & 0.05 & $\sim 10^7$ & \cite{Murray2011} \\
        UNH-RVAT \cite{Bachant2014-RVAT-baseline} & H & 3 & 0.28 & $\sim 10^6$ & \cite{Michelen2014} \\
        RM2 (present) & Tapered H & 3 & 0.07--0.12 & $\sim 10^6$ &
    \end{tabular}

@@

Geometric parameters for the 1:6 scale RM2 rotor were taken from the RM2 design
report \cite{Barone2011}, with the exception of the shaft diameter, which was
scaled from the SAFL RM2 model \cite{Hill2014}. Values for both the 1:6 and
full-scale designs are presented in Tab.~\ref{tab:turb-geom} and a drawing of
the turbine is shown in Fig.~\ref{fig:turbine-drawing}. The rotor
components---blades, struts, shaft, and center hub sections---were fabricated
from 6061-T6 aluminum, which was hardcoat anodized per MIL-8625-A, type III,
class 2 specifications. CAD models of the turbine are available from
\cite{Bachant2015-RM2-CAD}.

@@

Data collection runs were separated into individual tows, for which all
independent variables---tow speed, tip speed ratio, velocity probe
position---were held constant. These runs were grouped into logical test matrix
``sections,'' in which typically a single independent variable was varied. Test
matrix section names and descriptions are provided in the \texttt{README.md}
file of the experimental data and code repository \cite{Bachant2016-RM2-data}.
Tow speed and their corresponding turbine diameter and blade chord Reynolds
numbers are presented in Tab.~\ref{tab:re}.

>>>>

    \begin{tabular}{c|c|c|c|c|c}
        Name & Rotor type & $N$ & $c/R$ & $Re_D$ & Used in \\
        \hline
        Sandia 2 m \cite{Blackwell1976} &  Darrieus  & 2--3 & 0.06--0.09 & $\sim 10^6$ & \cite{Roh2013,Bedon2014} \\
        Sandia 5 m \cite{Sheldahl1977} &  Darrieus  & 3 & 0.08 & $\sim 10^6$ & \cite{Antheaume2008,Bedon2014} \\
        Sandia 17 m \cite{Worstell1978} & Darrieus  & 2 & 0.06 & $\sim 10^7$ & \cite{Para1988,Orlandi2015,Bedon2014} \\
        Sandia 34 m \cite{Ashwill1992} & Darrieus  & 2 & 0.05 & $\sim 10^7$ & \cite{Liu1992,Murray2011,Bedon2014}  \\
        Strickland \emph{et al.} \cite{Strickland1981} & H & 1--3 & 0.15 & $\sim 10^5$ & \cite{Ponta2001,Scheurich2011b} \\
        Laneville and Vitecoq \cite{Laneville1986} & H & 2 & 0.13 & $\sim 10^6$ & \cite{Amet2009} \\
        Howell \emph{et al.} \cite{Howell2010} & H & 2--3 & 0.33 & $\sim 10^5$ & \cite{Joo2015} \\
        Mertens \cite{Mertens2003} & H & 2 & 0.21 & $\sim 10^5$ & \cite{Orlandi2015} \\
        VAWT 850 \cite{Mays1990} & Tapered H & 2 & 0.05 & $\sim 10^7$ & \cite{Murray2011} \\
        UNH-RVAT \cite{Bachant2014-RVAT-baseline} & H & 3 & 0.28 & $\sim 10^6$ & \cite{Michelen2014} \\
        RM2 (present) & Tapered H & 3 & 0.07--0.12 & $\sim 10^6$ &
    \end{tabular}

@@

Geometric parameters for the 1:6 scale RM2 rotor were taken from the RM2 design
report \cite{Barone2011}, with the exception of the shaft diameter, which was
scaled from the SAFL RM2 model \cite{Hill2014}. Values for both the 1:6 and
full-scale designs are presented in Table~\ref{tab:turb-geom} and a drawing of
the turbine is shown in Fig.~\ref{fig:turbine-drawing}. The rotor
components---blades, struts, shaft, and center hub sections---were fabricated
from 6061-T6 aluminum, which was hardcoat anodized per MIL-8625-A, type III,
class 2 specifications. CAD models of the turbine are available from
\cite{Bachant2015-RM2-CAD}.

@@

Data collection runs were separated into individual tows, for which all
independent variables---tow speed, tip speed ratio, velocity probe
position---were held constant. These runs were grouped into logical test matrix
``sections,'' in which typically a single independent variable was varied. Test
matrix section names and descriptions are provided in the \texttt{README.md}
file of the experimental data and code repository \cite{Bachant2016-RM2-data}.
Tow speeds and their corresponding turbine diameter and blade chord Reynolds
numbers are presented in Table~\ref{tab:re}.
